---
title: "lab 7"
author: "Barbara Rose Hoover"
date: "11/13/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Hi it's BR
```{r}
library(tidyverse)
gc_df<-read.csv("gc_df.csv")

```

```{r}
get_guns<- gc_df %>% 
  filter(gender== "Male"| gender== "Female", make_get_guns !="") %>% 
  count(gender, make_get_guns) %>% 
  spread(make_get_guns, n) %>% 
  select(-gender)

rownames(get_guns)<-c("Female", "Male")

```

My name is Javier the collaborator and I'm going to be doing chi-square test for independence. 

We ask: "Is there a significant association between sex and opinion on whether guns should be more difficult, easier, or the same difficulty to get?" 

```{r}
#Let's look at the actual proportions: 

gun_prop <- prop.table(as.matrix(get_guns), 1)
gun_prop 

gun_x2 <- chisq.test(get_guns)
gun_x2
```

"Recommended government action on gun access differed significantly between male (n=...) and female (n=...) respondents ($\chi^2$(`r gun_x2$parameter`) = ....., p<0.001). Notably, a much higher proportion of female respondents (57.4%) recommend making it more difficult to get guns, compare to 40.4%"
